AMEN to Replication: Networks in IR

### 2016-11-25 amenIntro/amenIntro.Rmd
sync up

---
title: "Amen to replication: What have we learned about networks in International relations "
author: "Minhas, Dorff, Foster, Gallop, Liu, Roberts, Tellez, Ward"
output: 
      ioslides_presentation:
            smaller: true
---

>>>>

---
title: "AMEN to Replication: Networks in IR"
author: "Minhas, Dorff, Gallop, Foster, Liu, Roberts, Tellez, Ward"
output: 
      ioslides_presentation:
            smaller: true
---
